---
title: More impressive pandoc-ing
author: Michael Lerch
output: rmarkdown::tufte_handout
---

```{r setup, echo = FALSE, results = "hide", warning = FALSE, message = FALSE}
library(knitr)
options(digits = 2)
diamond <- read.csv("./data/diamond.csv")
```

Introduction
============

Objective 1
-----------

In this document, I will investigate diamond prices based on color and carat.

Objective 2
-----------

I also hope to demonstrate different pandoc output types.

Analysis
========

Average price
-------------

The overall average price is `r mean(diamond$Price)`

Investigating a linear relationship
-----------------------------------

Is there linear relationship between price and carat after accounting for
color?

```{r data, fig.margin = TRUE}
diamond <- read.csv("./data/diamond.csv")
plot(diamond$Price ~ diamond$Carat, col = diamond$Color, pch = 19,
     ylab = "Price", xlab = "Carat")
```

Log transform of price
----------------------

```{r plotlog, fig.margin=TRUE}
plot(log(diamond$Price) ~ diamond$Carat, col = diamond$Color, pch = 19,
     ylab = "log-Price", xlab = "Carat")
```

Final model
-----------

```{r model, results = "asis"}
lm1 <- lm(log(Price) ~ Carat * Color, data = diamond)
kable(data.frame(Value = coef(lm1)))
```

There is `r ifelse(summary(lm1)$coef[3, 4] < 0.05, print("significant"),
print("little"))`  evidence that the effect for color F on price is is non-zero
after accounting for carat.
